Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-15 article.tex
quadrant criterion explanations

Gabriel graphs are named after K. Ruben Gabriel, who introduced them in a paper with Robert R. Sokal in 1969 \cite{art_gabriel}.

@@

\subsubsection{Quadrant criterion}

>>>>

Gabriel graphs are named after K. Ruben Gabriel, who introduced them in a paper with Robert R. Sokal in 1969 \cite{10.2307/2412323}.

@@

\subsubsection{Quadrant criterion}
A version of this criterion, that was introduced here \cite{10201211} and used here \cite{art_del_paq}. Its goal is
to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
$k$-NN potential neigbours method.

It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours
in each of the quadrants. The number of quadrants has been fixed to 6 (optimized here \cite{art_del_paq}).

The criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between 0 and 
60 degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.

In other words, it tends to select the angle with which the potential neighbors are as much in the middle of their respective quadrants
as possible.

The quadrant criterion is illustrated here Fig~\ref{fig:crit_qua}
